---
title: "Linear Regression with Log Predictors"
author: "Bradley Wallace"
date: "08/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

QUESTION 1-8

For Questions 1-4: Create a linear regression model (using the lm function) with Sales as the dependent variable and Price as the independent variable. 

For Questions 5-8, create a linear regression model (using the lm function) with Sales as the dependent variable and Price, Bad_Shelf, and Good_Shelf as independent variables. 

Create two indicator (dummy) variables:

Bad_Shelf = 1 if ShelveLoc = “Bad”, 0 otherwise
Good_Shelf = 1 if ShelveLoc = “Good”, 0 otherwise


```{r carseats}
library(dplyr)
library(ISLR)
data1 <- Carseats
summary(data1)
str(data1)

lm1 <- lm(Sales ~ Price, data=data1)
summary(lm1)

data1 <- data1 %>%
  mutate(Bad_Shelf = as.factor(ifelse(ShelveLoc=="Bad",1,0)))

data1 <- data1 %>%
  mutate(Good_Shelf = as.factor(ifelse(ShelveLoc=="Good",1,0)))

str(data1)
lm2 <- lm(Sales ~ Price + Bad_Shelf + Good_Shelf, data=data1)
summary(lm2)

```

For questions 9-12, use the file PriceDemand.csv. Download it from here: https://www.dropbox.com/s/62jev2rnapxq6pw/PriceDemand.csv?dl=0 (Links to an external site.)

Background information: A consumer packaged goods firm is studying the sales of its flagship        brand of laundry detergent, CleanPill. We have weekly data over a 50-week period on units sold and retail price (in dollars) in a dataset called PriceDemand. 

Code to load the data set:  PriceDemand = read.csv("PriceDemand.csv", header = TRUE)

Fit a linear regression model with Qty as the response variable and Price as the explanatory variable. 

```{r pricedemand}
data2 <- read.csv("F:/Documents/PriceDemand.csv") # load data set
lm3 <- lm(Qty ~ Price, data=data2)
summary(lm3)

lm4 <- lm(Qty ~ log(Price), data=data2)
summary(lm4)

lm5 <- lm(log(Qty) ~ Price, data=data2)
summary(lm5)

lm6 <- lm(log(Qty) ~ log(Price), data=data2)
summary(lm6)
```

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
